---
title: "Excel User research_SEM"
output: 
  html_document: 
    keep_md: yes
---
Import the data and set up the packages:
```{r}
df <- read.csv("/Users/zhenyangcai/Downloads/YouTube SEM Series_2017_Cleaned.csv")
library(lavaan)
library(semPlot)
library(dplyr)
library(moments)
library(psych)
library(GPArotation)
```

Data cleaning:


Check the assumptions:

(1)Accuracy
```{r}
str(df)
summary(df)
```

All the items are numerical and ranges from 1-5, which is the right range, the only problem is the Gender variable, it should be a categorical variable instead of a numerical variable.

```{r}
df$Gender <- factor(df$Gender)
levels(df$Gender) <- c("Male", "Female")
```

(2) Missing
```{r}
any(is.na(df))
```
There are no missing values

(3)Outliers
```{r}
cutoff <- qchisq(1-.001, ncol(df))
mahal <- mahalanobis(select(df, Playful_1:DecQual_8), colMeans(select(df, Playful_1:DecQual_8)), cov(select(df, Playful_1:DecQual_8)))
NoMultiOutlier <- subset(df, mahal < cutoff)
Items <- select(NoMultiOutlier, Playful_1:DecQual_8)
nrow(NoMultiOutlier) # 361
nrow(Items)  # 380    19 cases are deleted
```

Check the multivariate outliers and found that the mahalnobis distance of 19 cases is higher than the cutoff value, so delete those cases.

(3) additivity: check the correlation matrix of the original data, make sure it;s not perfectly correlated.
```{r}
correl <- cor(Items, use = "pairwise.complete.obs")
symnum(correl)
```

No pairs of item are highly correlated.


(4)Linearity Normality Homogeneity  Homoscedasciticity
```{r}
#set up the assumptions
random <- rchisq(nrow(Items), 7)
## run a fake regression, we use all the variables to predict a series of random number
fake <- lm(random~., data = Items)
# Create the standardized residuals and scaled fitted values
standaridzed_residuals <- rstudent(fake)
fitted <- scale(fake$fitted.values)

#check the Normality
any(skewness(Items)>3)
kur <- kurtosis(Items)
a <- subset(Items, kur>3) # super kurtosis
hist(standaridzed_residuals) # looks decent

# Linearity: we use the qqplot
qqnorm(standaridzed_residuals)
abline(a=0,b=1)

#Homogeneity and Homoscedastivity
plot(fitted,standaridzed_residuals)
abline(0,0)
abline(v=0)
abline(h=2)
numberfactors <- fa.parallel(Items, fm = "ml", fa ="fa")
model <- fa(Items, nfactors = 6, rotate = "promax", fm="ml")
model2 <- fa(Items[ ,-c(36)], nfactors = 6, rotate = "promax", fm="ml")
model3 <- fa(Items[ ,-c(36,32,38)], nfactors = 6, rotate = "promax", fm="ml")
new_Items <- Items[ ,-c(36,32,38)]
new_NoMultiOutlier <- NoMultiOutlier[,-c(39,37,33)]
```


```{r}
cfi <- 1 - ((model3$STATISTIC - model3$dof)/
              (model3$null.chisq - model3$null.dof))
cfi
```


CFA:

```{r}
Excel_model_cfa <- '
Playful =~ Playful_1 + Playful_2 + Playful_3 + Playful_4 + Playful_5 + Playful_6 + Playful_7
AtypUse =~ AtypUse_1 + AtypUse_2 + AtypUse_3 + AtypUse_4 + AtypUse_5
Useful =~ Useful_1 + Useful_2 + Useful_3 + Useful_4 + Useful_5 + Useful_6 + Useful_7
Joy =~ Joy_1 + Joy_2 + Joy_3 + Joy_4 + Joy_5 + Joy_6 + Joy_7
InfoAcq =~ InfoAcq_1 + InfoAcq_2 + InfoAcq_3 + InfoAcq_4 + InfoAcq_5
DecQual =~ DecQual_2 + DecQual_3 + DecQual_4 + DecQual_7
'
cfa_path <- cfa(Excel_model_cfa, data = Items)
summary(cfa_path, 
        standardized=TRUE, 
        rsquare=TRUE, 
        fit.measure = TRUE)
semPaths(cfa_path)
```

Strutrual Model:
```{r}
Excel_model_path <- '
# measurement model
Playful =~ Playful_1 + Playful_2 + Playful_3 + Playful_4 + Playful_5 + Playful_6 + Playful_7
AtypUse =~ AtypUse_1 + AtypUse_2 + AtypUse_3 + AtypUse_4 + AtypUse_5
Useful =~ Useful_1 + Useful_2 + Useful_3 + Useful_4 + Useful_5 + Useful_6 + Useful_7
Joy =~ Joy_1 + Joy_2 + Joy_3 + Joy_4 + Joy_5 + Joy_6 + Joy_7
InfoAcq =~ InfoAcq_1 + InfoAcq_2 + InfoAcq_3 + InfoAcq_4 + InfoAcq_5
DecQual =~ DecQual_2 + DecQual_3 + DecQual_4 + DecQual_7

# regression
Useful ~ Playful + AtypUse
Joy ~ AtypUse + Playful
DecQual ~ Useful + AtypUse + Joy
InfoAcq ~ Useful + Playful + Joy
'
PathModel_1 <- sem(Excel_model_path, data = Items)
summary(PathModel_1, 
        standardized=TRUE, 
        rsquare=TRUE, 
        fit.measure = TRUE)
semPaths(PathModel_1, layout = "tree")
```


Mediation effect:
```{r}
Excel_model_mediation <- '
# measurement model
Playful =~ Playful_1 + Playful_2 + Playful_3 + Playful_4 + Playful_5 + Playful_6 + Playful_7
AtypUse =~ AtypUse_1 + AtypUse_2 + AtypUse_3 + AtypUse_4 + AtypUse_5
Useful =~ Useful_1 + Useful_2 + Useful_3 + Useful_4 + Useful_5 + Useful_6 + Useful_7
Joy =~ Joy_1 + Joy_2 + Joy_3 + Joy_4 + Joy_5 + Joy_6 + Joy_7
InfoAcq =~ InfoAcq_1 + InfoAcq_2 + InfoAcq_3 + InfoAcq_4 + InfoAcq_5
DecQual =~ DecQual_2 + DecQual_3 + DecQual_4 + DecQual_7

# regression
Useful ~ a*Playful + AtypUse
Joy ~ AtypUse + Playful
DecQual ~ Useful + AtypUse + Joy
InfoAcq ~ c*Useful + b*Playful + Joy
ind := a*c
'
mediaton <- sem(Excel_model_mediation, data = NoMultiOutlier)
summary(mediaton)
```

When setting Joy as the mediator, the result is partially mediated.


Moderation Effect: Do it in the SmartPLS




Multiple group:
# for cfa model
```{r}
#Subset the data and test the model fit within each data

items_men <- filter(new_NoMultiOutlier, Gender == "Male")
items_women <- filter(new_NoMultiOutlier, Gender == "Female")
men_fit <- sem(Excel_model_path, data = items_men, meanstructure=TRUE)
women_fit <- sem(Excel_model_path, data = items_women, meanstructure=TRUE)
summary(men_fit, fit.measures=T)
summary(women_fit, fit.measures=T)

# Test
library(semTools)
options(scipen = 999)
multisteps <- measurementInvariance(Excel_model_path, 
                                   data = new_NoMultiOutlier, 
                                   group = "Gender",
                                   strict = T )
```

The model does not break down, which means the female group and male group are pretty the same for the whole CFA model, then for each group cfa, it's still the same.

```{r}
means <- multisteps$fit.means
loadings <- parameterestimates(means)

menload <- subset(loadings, group == "1" & op == "=~", select = "est")  # loading for each item
womenload <- subset(loadings, group == "2" & op == "=~", select = "est")


menmultiply <- apply(items_men[,2:36], 1, function(x) { x * menload })
womenmultiply <- apply(items_women[,2:36], 1, function(x) { x * womenload })

menmultiply <- as.data.frame(menmultiply)
menmultiply <- t(menmultiply) ##flip it so it's people per row

womenmultiply <- as.data.frame(womenmultiply)
womenmultiply <- t(womenmultiply) ##flip it so it's people per row



men_Playful <- apply(menmultiply[ , c(1:7)], 1, mean)
men_AtypUse <- apply(menmultiply[ , c(8:12)], 1, mean)
men_Useful <- apply(menmultiply[ , c(13:19)], 1, mean)
men_Joy <- apply(menmultiply[ , c(20:26)], 1, mean)
men_InfoAcq <- apply(menmultiply[ , c(27:31)], 1, mean)
men_DecQual <- apply(menmultiply[ , c(32:35)], 1, mean)

women_Playful <- apply(womenmultiply[ , c(1:7)], 1, mean)
women_AtypUse <- apply(womenmultiply[ , c(8:12)], 1, mean)
women_Useful <- apply(womenmultiply[ , c(13:19)], 1, mean)
women_Joy <- apply(womenmultiply[ , c(20:26)], 1, mean)
women_InfoAcq <- apply(womenmultiply[ , c(27:31)], 1, mean)
women_DecQual <- apply(womenmultiply[ , c(32:35)], 1, mean)

t.test(men_Playful, women_Playful, 
       alternative = "two.sided", 
       paired=FALSE,
       var.equal = TRUE,
       na.action=TRUE)
t.test(men_Useful, women_Useful, 
       alternative = "two.sided", 
       paired=FALSE,
       var.equal = TRUE,
       na.action=TRUE)
t.test(men_AtypUse, women_AtypUse, 
       alternative = "two.sided", 
       paired=FALSE,
       var.equal = TRUE,
       na.action=TRUE)
t.test(men_Joy, women_Joy, 
       alternative = "two.sided", 
       paired=FALSE,
       var.equal = TRUE,
       na.action=TRUE)
t.test(men_InfoAcq, women_InfoAcq, 
       alternative = "two.sided", 
       paired=FALSE,
       var.equal = TRUE,
       na.action=TRUE)
t.test(men_DecQual, women_DecQual, 
       alternative = "two.sided", 
       paired=FALSE,
       var.equal = TRUE,
       na.action=TRUE)

```
















